\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-25 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively. At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, in the simulation conducted with {\it VR}=10, the formation of fingers can be noticed at early stages of the simulation.
\medskip
In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.

>>>>

Figures~\ref{fig:homoheleshaw_VN3} and \ref{fig:homoheleshaw_VN10} show fluid displacement in simulations conducted with {\it VR}=3 and {\it VR}=10, respectively. At relatively low viscosity ratio conditions (\ie {\it VR}=3), saturation evolves in time with a smooth front throughout most of the domain, and no finger could be observed. Elongated saturation profile at later stages of the simulation is due to pressure gradient near the sink region. However, formation of fingers can be noticed at early stages of the simulation conducted with {\it VR}=10.

In fig.\ref{fig:1a_homoheleshaw_3}(a), there is the description of the domain. Three different cases with different set-ups will follow. The first one is the homogeneous domain where permeability $K_{1}=1.e-10$ everywhere while for the heterogeneous case the following permeabilities have been introduced, $K_{1}=(1.e-10 \;to\; 5.e-10$), $K_{2}=1.e-10$, $K_{3}=(1.e-11 \;to\; 5.e-10)$ and $K_{4}=(1.e-12 \;to\; 5.e-10)$. For the homogeneous case we use two different mobility ratios of $3$ and $10$ while we proceed to the heterogeneous case using a mobility ratio of $10$.

### 2017-06-25 Papers/ViscousInstabilities/article_figure1.tex
updates on progress
updates

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{4.cm} (b) t=250\red{(???)} \hspace{2.5cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{3.0cm} (e) t=1000\red{(???)}   \hspace{4.cm} (f) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains \red{XX} \PN[1]{2} triangular elements. \red{(ADD SATURATION AND PRESSURE LEGENDS !!)}}
\label{fig:homoheleshaw_VN3}
\end{figure}
\end{landscape}
\clearpage

@@

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2.pdf}
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_250.pdf}
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_1000.pdf}}
\vspace{0.cm}
\hbox{\hspace{2.0cm} (a) pressure at t=0 \hspace{4.cm} (b) t=250\red{(???)} \hspace{2.5cm} (c) t=1000\red{(???)}}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_2500.pdf}
      \includegraphics[width=.35\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_3500.pdf} 
      \includegraphics[width=.67\textwidth]{./Pics1/Saffman_homogeneous_MR3/saffman_homo_fixed_end_1.pdf}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (d) t=2500\red{(???)} \hspace{4.0cm} (e) t=1000\red{(???)}   \hspace{2.5cm} (f) t=XXX\red{(???)}}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=3): (a) pressure profile \red{(is it true?}) $\left(\text{in g.cm}^{-1}\text{.s}^{-2}\right)$ with source and sink regions are explicitly shown along with dimensions (in cm); (b-f) snapshots of wetting phase saturation showing flow profile as the simulation evolves. The domain contains \red{XX} \PN[1]{2} triangular elements. \red{(ADD SATURATION AND PRESSURE LEGENDS !!)}}
\label{fig:homoheleshaw_VN3}
\end{figure}
\end{landscape}
\clearpage

@@

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) t=0\red{??} \hspace{3.cm} (b) t=500\red{(???)} \hspace{3.0cm} (c) t=2000\red{(???)}}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{3.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$. The domain contains \red{XXXX} elements.}
\label{HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage
